Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-01-08 joss/paper.Rmd
Adds text on provenance

>>>>

The provenance of the results can be seen as terminal nodes. This
information is based on the static analysis of the script, which
traces the relationship among code lines from inputs to
outputs. This is the information that forms the basis of the code reduction
techinque at the heart of Rclean. Because we can predict what lines of
code results depend, or more relevantly *don't* depend, allows us to
predict what code can be removed from a given script. Thus, when we
know what results we really want, we can rely on the formalized
provenance to automatically plot a course of "pruning" through the
script to trim out what we no longer need.
